DOpElib:\\ Differential Equations and Optimization Environment

### 2016-04-01 Examples/Documentation/introduction.tex
Removed old makefiles parts

When installing \texttt{deal.II} you should take care to configure 
it to use UMFPACK, i.e.,\\
\texttt{./configure --with-umfpack}
in version up to 7.3.0. From 8.0.0 on, deal.II is compiled with 
cmake, which makes the inclusion of external packages easier.
Detailed installing instructions for deal.II can be found on\\ 
\texttt{http://www.dealii.org/}.

In deal.II 8 and newer a configuration of deal.II working with \texttt{DOpElib} can be done with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install -DDEAL_II_WITH_UMFPACK=true -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags

>>>>

When installing \texttt{deal.II} (at least version 8.0) you should take care to configure 
it to use UMFPACK.

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install -DDEAL_II_WITH_UMFPACK=true -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags
